Process_OlisSpectraJazEmData

### 2024-01-05 Code/Process_OlisJazEmData.Rmd
Fixing variable names so that Baltic and PICO projects are same

#Left off here
```{r}
JazEmFile <- JazEmFile %>% 
  filter(MC_SpectralID != "MCMIX004_WW",
         MCSetPar_uE == 30 ) %>% 
  select(-c( FilenameJaz, MC)) %>% 
  unnest(Spectra) %>%  
  group_by(WL) %>% 
  mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
ungroup()
```

>>>>

# Filter out the white light emission data for mixed light color MC since not used. Calculate MC normalized emission to the emission maxima for each wavelength.
```{r calculate normalized emission for each WL}
JazEmFile <- JazEmFile %>% 
  filter(MC_SpectralID != "MCMIX004_WW",
         MCSetPar_uE == 30 |
         MCSetPar_uE == 15) %>% 
  select(-c( FilenameJaz, MC)) %>% 
  unnest(Spectra) %>%  
  group_by(WL) %>% 
  mutate(MC_NormEm = round(Emission / Emission[which.max(Emission)], digits = 4)) %>% 
  select(-c(ObsDate)) %>% 
ungroup()
```

# Unnest the Olis whole cell absorbance data and extract absorbance maxima for 675 nm (red) and 450 (blue) regions and extract nm (wavelength) at that absorbance maxima 
```{r}
OLISSpectraUnnest <- OLISSpectraFile %>% 
  unnest(AbsSpectra)

OlisSpectra_red <- OLISSpectraUnnest %>% 
  group_by(SampleID, E_days) %>%
  filter(OlisAbs_nm >= 625 & OlisAbs_nm <= 750) %>% 
   mutate(RedMaxima_nm = round(OlisAbs_nm[which.max(Absorbance)]),
          MaxAbs_Red = Absorbance[which.max(Absorbance)]) %>% 
  filter(OlisAbs_nm == 675) %>% # filter only 675 nm to get df that matches the nested df to join
  select(SampleID, Run, Strain, RedMaxima_nm, MaxAbs_Red, Par_ue, E_days) %>% 
     ungroup()

OlisSpectra_blue <- OLISSpectraUnnest %>% 
  group_by(SampleID, E_days) %>%
  filter(OlisAbs_nm >= 400 & OlisAbs_nm <= 460) %>% 
   mutate(BlueMaxima_nm = round(OlisAbs_nm[which.max(Absorbance)]),
          MaxAbs_Blue = Absorbance[which.max(Absorbance)])  %>% 
  filter(OlisAbs_nm == 440) %>% # filter only 440 nm to get df that matches the nested df to join
  select(SampleID, Run, Strain, BlueMaxima_nm, MaxAbs_Blue,  Par_ue, E_days) %>% 
  ungroup()

 OlisSpectraMeta <- left_join(OLISSpectraFile, OlisSpectra_red)
 OlisSpectraMeta <- left_join(OlisSpectraMeta, OlisSpectra_blue)

remove(OlisSpectra_red)
remove(OlisSpectra_blue)
remove(OLISSpectraUnnest)

# Left join Olis whole cell absorbance data with Jaz MC emission data. Emission measurements were performed on the mixed color MCMIX004 and the white light MC257
```{r join whole cell absorbance with MC emission data}

OlisSpectraMeta <- OlisSpectraMeta %>% 
  unnest(AbsSpectra)

OlisJazMetaData <- left_join(OlisSpectraMeta, JazEmFile, by = c("WL", "OlisAbs_nm" = "MCEm_nm")) %>% 
  mutate(MCEm_nm = OlisAbs_nm)

remove(OlisSpectraMeta)
remove(JazEmFile)
remove(OLISSpectraFile)
```

# Normalization. Used max peak of each spectra to normalize peaks to red Chla region (625 to 750 nm) and blue Chla region (400 to 460 nm).
```{r normalization }

OlisJazMetaData <- OlisJazMetaData %>% 
  group_by(SampleID, E_days) %>%
 mutate(AbsNorm440 = Absorbance / MaxAbs_Blue,
        AbsNorm675 = Absorbance / MaxAbs_Red) %>% 
  ungroup()

glimpse(OlisJazMetaData)
```

# Calculate Photosynthetic Usable Radiation (PUR) from MC normalized emission and normalized Olis whole cell absorbance spectrums.  
```{r PUR}
OlisJazMetaData <- OlisJazMetaData %>%
    filter(OlisAbs_nm >= 400 &
           OlisAbs_nm <= 700) %>%
  mutate(PURAbsWholeCell_Norm = MC_NormEm * AbsNorm440) %>% 
  group_by(ID, E_days) %>% 
  mutate(SumPURAbsWholeCell_Norm = sum(MC_NormEm * AbsNorm440),
         Pur_ue = round(Par_ue * (SumPURAbsWholeCell_Norm / sum(MC_NormEm))),
         ParPurRatio = sum(MC_NormEm) / SumPURAbsWholeCell_Norm,
         PurParRatio =  SumPURAbsWholeCell_Norm / sum(MC_NormEm)) %>% 
ungroup() %>% 
  select(-SumPURAbsWholeCell_Norm)

glimpse(OlisJazMetaData)
